Near Optimal Behavior via Approximate State Abstraction

### 2016-05-24 paper/example_domains.tex
Doing some compressions for spcae
prepping for merge

%Description of code base
Our code base (link redacted for review) provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}.

>>>>

%Description of code base
Our code base\footnote{Available here: \url{github.com/david-abel/state_abstraction}} provides implementations for abstracting arbitrary \acp{MDP} as well as visualizing and evaluating the resulting abstract \acp{MDP}. We use the graph-visualization library GraphStream~\cite{graphstream} and the planning and \ac{RL} library, BURLAP\footnote{http://burlap.cs.brown.edu/}. For all experiments, we set $\gamma$ to $0.95$.
